---
title: "MechaCar Statistical Analysis Notebook"
output: html_notebook
---

**Pre-requisite**

You will need R install on your computer and an IDE. R Studio is recommended. You should also install tidyverse with ***install.packages("tidyverse")***. This will install the core tidyverse packages that you are likely to use in almost every analysis:

-   [ggplot2](https://ggplot2.tidyverse.org/), for data visualisation.

-   [dplyr](https://dplyr.tidyverse.org), for data manipulation.

-   [tidyr](https://tidyr.tidyverse.org), for data tidying.

-   [readr](https://readr.tidyverse.org/), for data import.

-   [purrr](https://purrr.tidyverse.org/), for functional programming.

-   [tibble](https://tibble.tidyverse.org), for tibbles, a modern re-imagining of data frames.

```{r}
# 1a. Load the dplyr package
library(dplyr)
```

```{r}
# 1b. Load the tidyverse package
library(tidyverse)
```

```{r}
# 2. Import and read in the MechaCar_mpg.csv file as a dataframe.
mecha_mpg <- read.csv(file='./Resources/Data/MechaCar_mpg.csv',check.names=F,stringsAsFactors = F) 
```

```{r}
# 3. Run linear regression on all six variables(i.e., columns), and add the dataframe as the data parameter.

lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data=mecha_mpg)

```

```{r}
# 6. Using the summary() function, determine the p-value and the r-squared value for the linear regression model.

summary(lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data=mecha_mpg)) 

```

```{r}
# Optional step:

lm(mpg ~ vehicle_length + ground_clearance, data=mecha_mpg)
summary(lm(mpg ~ vehicle_length + ground_clearance, data=mecha_mpg)) 
```

```{r}

```
