---
title: "MechaCar Statistical Analysis Notebook"
output: html_notebook
---

Note: This is a R Notebook which outputs a companion file MechaCarChallenge.nb.html when the Notebook is run.

### **Pre-requisite** 

You will need R install on your computer and an IDE. R Studio is recommended. You should also install tidyverse with ***install.packages("tidyverse")***. This will install the core tidyverse packages that you are likely to use in almost every analysis:

-   [ggplot2](https://ggplot2.tidyverse.org/), for data visualisation.

-   [dplyr](https://dplyr.tidyverse.org), for data manipulation.

-   [tidyr](https://tidyr.tidyverse.org), for data tidying.

-   [readr](https://readr.tidyverse.org/), for data import.

-   [purrr](https://purrr.tidyverse.org/), for functional programming.

-   [tibble](https://tibble.tidyverse.org), for tibbles, a modern re-imagining of data frames.

### **Deliverable 1: Linear Regression to Predict MPG**

The `MechaCar_mpg.csv` dataset contains mpg test results for 50 prototype MechaCars. The MechaCar prototypes were produced using multiple design specifications to identify ideal vehicle performance. Multiple metrics, such as vehicle length, vehicle weight, spoiler angle, drivetrain, and ground clearance, were collected for each vehicle.

```{r}
# 1a. Load the dplyr package
library(dplyr)
```

```{r}
# 1b. Load the tidyverse package
library(tidyverse)
```

```{r}
# 2. Import and read in the MechaCar_mpg.csv file as a dataframe.
mecha_mpg <- read.csv(file='./Resources/Data/MechaCar_mpg.csv',check.names=F,stringsAsFactors = F) 
```

```{r}
# 3. Run linear regression on all six variables(i.e., columns), and add the dataframe as the data parameter.

lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data=mecha_mpg)

```

```{r}
# 4. Using the summary() function, determine the p-value and the r-squared value for the linear regression model.

summary(lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data=mecha_mpg)) 

```

```{r}
# Optional Steps: Remove the independent variables that have little impact on predicting mpg to see impact

lm(mpg ~ vehicle_length + ground_clearance, data=mecha_mpg)
summary(lm(mpg ~ vehicle_length + ground_clearance, data=mecha_mpg)) 
```

### **Deliverable 2: Create Visualizations for the Trip Analysis**

The MechaCar `Suspension_Coil.csv` dataset contains the results from multiple production lots. In this dataset, the weight capacities of multiple suspension coils were tested to determine if the manufacturing process is consistent across production lots.

```{r}
# 1. Import and read in the Suspension_Coil.csv file as a table
mecha_coil <- read.csv(file='./Resources/Data/Suspension_Coil.csv',check.names=F,stringsAsFactors = F) 
```

```{r}
# 2. Create a total_summary dataframe in order to derive mean, median, variance, and standard deviation of the suspension coil’s PSI column

total_summary <- mecha_coil %>% summarize(Mean_PSI=mean(PSI),
                                          Median_PSI=median(PSI),
                                          Var_PSI=var(PSI),
                                          Std_Dev_PSI=sd(PSI),
                                          Num_Coil=n(), .groups = 'keep')
```

```{r}
# 3. Create a lot_summary dataframe in order to to group each manufacturing lot by the mean, median, variance, and standard deviation of the suspension coil’s PSI column.

lot_summary <- mecha_coil  %>% group_by(Manufacturing_Lot) %>% summarize(Mean_PSI=mean(PSI),
                                          Median_PSI=median(PSI),
                                          Var_PSI=var(PSI),
                                          Std_Dev_PSI=sd(PSI),
                                          Num_Coil=n(), .groups = 'keep')        
```

```{r}
# 4. Graph Box plot PSI Whole lot
plt1 <- ggplot(mecha_coil,aes(y=PSI)) #import dataset into ggplot2
plt1 + geom_boxplot() #add boxplot

```

```{r}

# box plot: PSI each individual Lot
plt2 <- ggplot(mecha_coil,aes(x=Manufacturing_Lot,y=PSI)) #import dataset into ggplot2
plt2 + geom_boxplot()
```

### **Deliverable 3:  T-Tests on Suspension Coils**

Perform t-tests to determine if all manufacturing lots and each lot individually are statistically different from the population mean of 1,500 pounds per square inch.

```{r}
# 1. Use the t.test() function to determine if the PSI across all manufacturing lots is statistically different from the population mean of 1,500 pounds per square inch.

t.test(mecha_coil$PSI,mu=1500)
```

```{r}
# 2. Use the t.test() function and its subset() argument to determine if the PSI for each manufacturing lot is statistically different from the population mean of 1,500 pounds per square inch.

# create the functions
lot1 <- subset(mecha_coil, Manufacturing_Lot=="Lot1")
lot2 <- subset(mecha_coil, Manufacturing_Lot=="Lot2")
lot3 <- subset(mecha_coil, Manufacturing_Lot=="Lot3")

# envoke the functions 
t.test(lot1$PSI,mu=1500)
t.test(lot2$PSI,mu=1500)
t.test(lot3$PSI,mu=1500)
```
